---
pagetitle: Edges
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### We can also customize edges with a lot of options, and by the same ways as nodes.

## Individual configuration

As seen in introduction, *edges* mut be a data.frame, with at least ```from``` and ```to``` columns, which make the link with ```id``` of nodes. You can add properties simply adding variables on data.frame. See **?visEdges** for available options. 

The most used are presented in the following example :

```{r}
edges <- data.frame(from = sample(1:10,8), to = sample(1:10, 8),
                    
  # add labels on edges                  
  label = paste("Edge", 1:8),
  
  # length
  length = c(100,500),
  
  # width
  width = c(4,1),
  
  # arrows
  arrows = c("to", "from", "middle", "middle;to"),
  
  # dashes
  dashes = c(TRUE, FALSE),
  
  # tooltip (html or character)
  title = paste("Edge", 1:8),
  
  # smooth
  smooth = c(FALSE, TRUE),
  
  # shadow
  shadow = c(FALSE, TRUE, FALSE, TRUE)) 

# head(edges)
#  from to  label length    arrows dashes  title smooth shadow
#    10  7 Edge 1    100        to   TRUE Edge 1  FALSE  FALSE
#     4 10 Edge 2    500      from  FALSE Edge 2   TRUE   TRUE

nodes <- data.frame(id = 1:10, group = c("A", "B"))
```

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%")
```

## Global configuration

If you want to set some configuration for all edges, it's possible in a simpler way, using directly **visEdges** function :

```{r}
nodes <- data.frame(id = 1:4)
edges <- data.frame(from = c(2,4,3,2), to = c(1,2,4,3))

visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(shadow = TRUE,
           arrows =list(to = list(enabled = TRUE, scaleFactor = 2)),
           color = list(color = "lightblue", highlight = "red")) %>%
  visLayout(randomSeed = 12) # to have always the same network           
```

Finally, you can also combine individual and global options : 

```{r}
nodes <- data.frame(id = 1:4, label = 1:4)
edges <- data.frame(from = c(2,4,3,2), 
                    to = c(1,2,4,3), 
                    dashes = c(TRUE, FALSE))

visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(shadow = TRUE,
           arrows =list(to = list(enabled = TRUE, scaleFactor = 2)),
           color = list(color = "lightblue", highlight = "red")) %>%
  visLayout(randomSeed = 12) # to have always the same network             
```

## Use complex configuration individually

Available since __visNetwork_0.2.1__. When options are available using a list, you can use it in a data.frame with specific notation like this : 


```{r}
nodes <- data.frame(id = 1:3, 
                    color.background = c("red", "blue", "green"),
                    color.highlight.background = c("red", NA, "red"), 
                    shadow.size = c(5, 10, 15))

edges <- data.frame(from = c(1,2), to = c(1,3),
                    label = LETTERS[1:2], 
                    font.color =c ("red", "blue"), 
                    font.size = c(10,20))

visNetwork(nodes, edges)  
```