---
pagetitle: Igraph
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### Since __visNetwork_0.2.1__, it's possible to make the link between the features of package [igraph](http://igraph.org/r/) and those of __visNetwork__ : 

* Use [igraph](http://igraph.org/r/) layout to compute coordinates for fast rendering with ``visIgraphLayout()``
* Transform [igraph](http://igraph.org/r/) network to __visNetwork__ network using ``visIgraph()`` or ``toVisNetworkData()``


## Use [igraph](http://igraph.org/r/) layout

With ``visIgraphLayout()``, you can use all available layouts in [igraph](http://igraph.org/r/) and calculate coordinates before the sending to [vis.js](http://visjs.org/) : 

```{r, eval = TRUE}
nnodes <- 100
nnedges <- 200

nodes <- data.frame(id = 1:nnodes)
edges <- data.frame(from = sample(1:nnodes, nnedges, replace = T),
                    to = sample(1:nnodes, nnedges, replace = T))

# with defaut layout
visNetwork(nodes, edges, height = "500px") %>%
  visIgraphLayout() %>%
  visNodes(size = 10)
```

```{r, eval = TRUE}
# in circle ?
visNetwork(nodes, edges, height = "500px") %>%
  visIgraphLayout(layout = "layout_in_circle") %>%
  visNodes(size = 10) %>%
  visOptions(highlightNearest = T, nodesIdSelection = T)
```

## Use [igraph](http://igraph.org/r/) network 

``visIgraph`` transform directly a [igraph](http://igraph.org/r/) network into a __visNetwork__. It's a little bit experimental (not perfect). You can also use ``toVisNetworkData`` to just get data into __visNetwork__ format : 


```{r, eval = TRUE, fig.width = 10, fig.height = 10}
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
igraph_network <- graph.famous("Walther")

plot(igraph_network)
```

```{r, eval = TRUE}
# get data and plot :
data <- toVisNetworkData(igraph_network)
visNetwork(nodes = data$nodes, edges = data$edges, height = "500px")

# or plot directly
visIgraph(igraph_network)
```