---
pagetitle: Use image & Icon
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### Besides the various shapes, it's also possible to use **images** and **icons** for nodes.

## Images

* For use images in nodes, you first have to set ````shape```` to **image** or **circularImage**.
* Then, set the path relative or absolute on ````image```` value
* An option is available in case of wrong path : ````brokenImage````
* And you can use borders with ````shapeProperties```` and ````useBorderWithImage````

```{r}
path_to_images <- "https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/img/indonesia/"
 
nodes <- data.frame(id = 1:4, 
                    shape = c("image", "circularImage"),
                    image = paste0(path_to_images, 1:4, ".png"),
                    label = "I'm an image")
  
edges <- data.frame(from = c(2,4,3,3), to = c(1,2,4,2))

visNetwork(nodes, edges, width = "100%") %>% 
  visNodes(shapeProperties = list(useBorderWithImage = TRUE)) %>%
  visLayout(randomSeed = 2)
```


## fontAwesome icons

Actually, **visNetwork** supports [fontAwesome](http://fortawesome.github.io/Font-Awesome) icons. Font-awesome is not part of default dependencies, but you can use **addFontAwesome()** if needed.

* For use icons in nodes, you first have to set ````shape```` to **icon**.
* **icon** options must be a list, so you have to use **visNodes** or **visGroups**. (Can't be use with data.frame...)
* Choose the icon by his ````code````, set ````size```` and ````color````


```{r}
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))

visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "A", shape = "icon", 
            icon = list(code = "f0c0", size = 75)) %>%
  visGroups(groupname = "B", shape = "icon", 
            icon = list(code = "f007", color = "red")) %>%
  addFontAwesome()
```

