---
pagetitle: Introduction
---

## Introduction

**visNetwork** is a R package for network visualization, using **vis.js** javascript library (http://visjs.org/). All the remarks and bugs returns are welcome on github : https://github.com/DataKnowledge/visNetwork.

## Features

## Installation

Package is now available on CRAN.

```{r, eval=FALSE}
install.packages("visNetwork")

# can have new features in developpement version 
devtools::install_github("dataknowledge/visNetwork")
```

## How it's works ?

**visNetwork** needs at least two informations :

* a nodes data.frame, with *id* column
* a edges data.frame, with *from* and *to* columns

```{r}
require(visNetwork, quietly = TRUE)
# minimal example
nodes <- data.frame(id = 1:3)
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges, width = "100%")
```

## Find help ?

Besides the help R functions, a vignette is available, and you can access and read the full javascript API from R using  **visDocumentation()**:

```{r, eval = FALSE}
visDocumentation()
vignette("Introduction-to-visNetwork") # with CRAN version
```



