---
pagetitle: Introduction
---

## Introduction

**visNetwork** is an R package for network visualization, using **vis.js** javascript library (http://visjs.org/). All remarks and bugs are welcome on github : https://github.com/datastorm-open/visNetwork.

## Features

Based on [htmlwidgets](http://www.htmlwidgets.org/), so :

* compatible with [shiny ](http://shiny.rstudio.com/),  R Markdown documents, and RStudio viewer

The package proposes all the features available in **vis.js** API, and even more with special features for R : 

* easy to use
* custom shapes, styles, colors, sizes, ...
* works smooth on any modern browser for up to a few thousand nodes and edges
* interactivity controls (highlight, collapsed nodes, selection, zoom, physics, movement of nodes, tooltip, events, ...)
* visualize ``rpart`` tree

```{r, eval  = TRUE, echo = FALSE}
require(visNetwork, quietly = TRUE)
require(rpart, quietly = TRUE)

# Basic regression tree
res <- rpart(Petal.Length~., data=iris)
visTree(res, edgesFontSize = 14, nodesFontSize = 16, width = "100%")
```

## Installation

Package is now available on CRAN.

```{r, eval=FALSE}
install.packages("visNetwork")

# can have new features in development version 
devtools::install_github("datastorm-open/visNetwork")
```

## How does it work ?

**visNetwork** needs at least two pieces of information :

* a nodes _data.frame_, with ```id``` column
* an edges _data.frame_, with ```from``` and ```to``` columns, which make the link with ```id```

```{r}
require(visNetwork, quietly = TRUE)
# minimal example
nodes <- data.frame(id = 1:3)
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges, width = "100%")
```

## Need help ?

Besides the help R functions, a vignette is available, and you can access and read the full javascript API from R using  **visDocumentation()**:

```{r, eval = FALSE}
visDocumentation()
vignette("Introduction-to-visNetwork") # with CRAN version
# shiny example
shiny::runApp(system.file("shiny", package = "visNetwork"))
```



