---
title: "visNetwork"
output: html_document
---

**visNetwork** is a R package for network visualization, using **vis.js** javascript library (http://visjs.org/). All the remarks and bugs returns are welcome on github : https://github.com/DataKnowledge/visNetwork.

## Installation

Package is actually only available on github. You can install it with :

```{r, eval=FALSE}
devtools::install_github("DataKnowledge/visNetwork")
```

## Minimal example

**visNetwork** needs at least two informations :

* a nodes data.frame, with *id* column
* a edges data.frame, with *from* and *to* columns

```{r}
require(visNetwork, quietly = TRUE)
# minimal example
nodes <- data.frame(id = 1:3)
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges, width = "100%")
```


## More variables
You can add informations and customize network simply using more variables on nodes and edges data.frames. For example :

* *label* column : add labels on nodes / edges
* *value* column : control size on nodes / edges
* *title* column : add tooltip  on nodes / edges (html, or character)
* *group* column : Only for nodes. Add nodes groups.
* ...

```{r}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = trunc(runif(nb)*(nb-1))+1,
 to = trunc(runif(nb)*(nb-1))+1,
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))

visNetwork(nodes, edges, width = "100%")
```

## Nodes / edges options
Several global options are available for nodes and edges using *visNodes* and *visEdges*.
```{r net}
# change shape and color of nodes
# and style of edges
nodes <- data.frame(id = 1:3)
edges <- data.frame(from = c(1,2), to = c(3,3))
visNetwork(nodes, edges) %>% 
  visNodes(shape = "square", color = "darkblue") %>%
  visEdges(style ="dash-line")
```

## Groups options
You can use options per group using *visGroups*.
```{r}
nodes <- data.frame(id = 1:5,  
                    group = sample(c("A", "B"), 5, replace = TRUE))
edges <- data.frame(from = c(2,5,3), to = c(1,2,4))

visNetwork(nodes, edges, width = "100%") %>%
 visGroups(groupname = "A", color = "red", shape = "database") %>%
 visGroups(groupname = "B", color = "yellow", shape = "label")
```

# Network Options
A lot of configuration options are available in *visOptions* :


```{r, echo=FALSE}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = trunc(runif(nb)*(nb-1))+1,
 to = trunc(runif(nb)*(nb-1))+1,
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```

## Highlight nearest
Highlight nearest nodes and edges clicking on a node :

```{r}
visNetwork(nodes, edges, width = "100%") %>% visOptions(highlightNearest = TRUE)
```

## Add legend on groups
```{r}
visNetwork(nodes, edges, width = "100%",  legend = TRUE)
```

## Select by node id
```{r}
visNetwork(nodes, edges, width = "100%") %>% visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)
```

## Directed Network
```{r, echo = FALSE}
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(1:nb, nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = trunc(runif(nb)*(nb-1))+1,
 to = trunc(runif(nb)*(nb-1))+1,
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```

```{r}
visNetwork(nodes, edges, width = "100%") %>% visEdges(style = "arrow")
```

## Custom navigation
*vis.js* propose some navigation tools :

```{r}
visNetwork(nodes, edges, width = "100%") %>% visOptions(navigation = TRUE)
```

## Data Manipulation
And some data manipulation tools :

```{r}
visNetwork(nodes, edges, width = "100%") %>% visOptions(dataManipulation = TRUE)
```

## Hierarchical Layout
You can use and control hierarchical layout with *visHierarchicalLayout* :

```{r, echo = FALSE}
nodes <- data.frame(id = 1:7)

edges <- data.frame(from = c(1,2,2,2,3,3),
 to = c(2,3,4,5,6,7))
```

```{r}
visNetwork(nodes, edges, width = "100%") %>% visEdges(style = "arrow") %>% 
  visHierarchicalLayout(layout = "direction")

visNetwork(nodes, edges, width = "100%") %>% visEdges(style = "arrow") %>% 
  visHierarchicalLayout(direction = "LR", layout = "direction")
```

## Freeze network
```{r}
visNetwork(nodes, edges, width = "100%") %>% visOptions(dragNetwork = FALSE, dragNodes = FALSE)
```

## Clustering
```{r}
nodes <- data.frame(id = 1:10)
edges <- data.frame(from = round(runif(12)*10), to = round(runif(12)*10))

visNetwork(nodes, edges, width = "100%") %>%
 visClustering(initialMaxNodes = 5, nodeScaling = list(width = 50, height = 50, radius = 50))
```

# Additional features

## Export

```{r, eval = FALSE}
network <- visNetwork(nodes, edges, width = "100%")
htmlwidgets::saveWidget(network, "network.html")
```

## Use DOT language data 

```{r}
visNetwork(dot = 'dinetwork {1 -> 1 -> 2; 2 -> 3; 2 -- 4; 2 -> 1 }', width = "100%")
```

## Use gephi json export file

```{r, eval = FALSE}
# don't run here
visNetwork(gephi = 'WorldCup2014.json')
```

## Physics, tooltip, events, shiny, ...

You can also control :

* physics of network : *visPhysics*
* tootlip : *visTooltips*
* events : *visEvents*

And use in shiny apps with *visNetworkOutput* and *renderVisNetwork*

