---
pagetitle: Interactions
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### It's possible to control the network interaction with **visInteraction()** :

```{r, echo=FALSE}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = c(8,2,7,6,1,8,9,4,6,2),
 to = c(3,7,2,7,9,1,5,3,2,9),
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```


## Frozen network

* ````dragNodes```` : enabled or not the selection and movement of nodes (click on a node, and move your mouse)?
* ````dragView```` : enabled or not the movement of the full newtwork (click everywhere except node, and move your mouse) ?
* ````zoomView```` : enabled or not the zoom (use mouse scroll) ?

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visInteraction(dragNodes = FALSE, 
                 dragView = FALSE, 
                 zoomView = FALSE) %>%
  visLayout(randomSeed = 123)
```

## Hide edges/nodes on drag

Can increase the performance.

* ````hideEdgesOnDrag```` : hide egdes when dragging the view
* ````hideNodesOnDrag```` : hide nodes when dragging the view

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visInteraction(hideEdgesOnDrag = TRUE) %>%
  visLayout(randomSeed = 123)
```

## Navigation buttons

We can navigation buttons with ````navigationButtons```` :

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visInteraction(navigationButtons = TRUE)
```

## And also...

* ````keyboard```` : enabled keyboard manipulation rather than mouse (click on network before)
* ````hover```` and ````hoverConnectedEdges```` : control hover 
* ````selectable```` : disabled nodes and edges selection
* ````tooltipDelay```` : set delay before show pop-up
* ...

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visInteraction(keyboard = TRUE, tooltipDelay = 0)
```
