---
pagetitle: Layout
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### The layout is configurable with  **visLayout()** and **visHierarchicalLayout()** functions. 

## Set seed

The nodes are randomly positioned initially. This means that the settled result is different every time. You can provide a random seed manually (````randomSeed````), then the layout will be the same every time.

## Hierarchical Layout

You can use and control hierarchical layout with some options : 

* ````levelSeparation````, the distance between the different levels.
* ````direction````, the direction of the hierarchical layout. 
* ````sortMethod````, the algorithm used to ascertain the levels of the nodes based on the data

```{r, echo = TRUE}
nodes <- data.frame(id = 1:7)
edges <- data.frame(from = c(1,2,2,2,3,3),
 to = c(2,3,4,5,6,7))
```

```{r}
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrow = "from") %>% 
  visHierarchicalLayout() # same as   visLayout(hierarchical = TRUE) 
```

```{r}
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrow = "from") %>% 
  visHierarchicalLayout(direction = "LR", levelSeparation = 500)
```

it's also possible to define the ````level```` of each node :

```{r, echo = TRUE}
nodes <- data.frame(id = 1:4, level = c(2, 1, 1, 1))
edges <- data.frame(from = c(1, 1, 1),
 to = c(2,3,4))
```

```{r}
### with level
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrow = "from") %>% 
  visHierarchicalLayout() # same as   visLayout(hierarchical = TRUE) 
```

```{r}
### without level (vis.js choice)
nodes$level <- NULL
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrow = "from") %>% 
  visHierarchicalLayout() # same as   visLayout(hierarchical = TRUE) 
```