---
pagetitle: Legend
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

## Title

since __visNetwork_0.2.2__, you can add a title (``main``) to your network :

```{r}
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))

# default, on group
visNetwork(nodes, edges, main = "A really simple example", width = "100%")
```


## Legend based on groups

We can simply add a legend, based on the definition of groups, using **visLegend** : 

```{r}
# default, on group
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "A", color = "red") %>%
  visGroups(groupname = "B", color = "lightblue") %>%
  visLegend()
```

## Placement & title

It's also possible to adjust ````position```` (left or right), and ````width````, and add a title (``main``, since __visNetwork_0.2.2__) : 

```{r}
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "A", color = "red") %>%
  visGroups(groupname = "B", color = "lightblue") %>%
  visLegend(width = 0.1, position = "right", main = "Group")
```

## Custom nodes/edges

Since **0.1.2**, you can add custom nodes (````addNodes````) and/or edges (````addEdges````) on the legend : 

```{r}
# nodes data.frame for legend
lnodes <- data.frame(label = c("Group A", "Group B"),
 shape = c( "ellipse"), color = c("red", "lightblue"),
 title = "Informations", id = 1:2)

# edges data.frame for legend
ledges <- data.frame(color = c("lightblue", "red"),
 label = c("reverse", "depends"), arrows =c("to", "from"))
 
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "A", color = "red") %>%
  visGroups(groupname = "B", color = "lightblue") %>%
  visLegend(addEdges = ledges, addNodes = lnodes, useGroups = FALSE)
```

Finally, it's possible to use definition of the groups (````useGroups = TRUE #default````) with  custom nodes (````addNodes````) and/or edges (````addEdges````) : 

```{r}
ledges <- data.frame(color = c("lightblue", "red"),
 label = c("reverse", "depends"), arrows =c("to", "from"))
 
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "A", color = "red") %>%
  visGroups(groupname = "B", color = "lightblue") %>%
  visLegend(addEdges = ledges, useGroups = TRUE) 
```

For more complex elements, if you prefer, you can use a **list** instead of **data.frame** : 

```{r}
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))

visNetwork(nodes, edges) %>%
 visGroups(groupname = "A", shape = "icon", 
           icon = list(code = "f0c0", size = 75)) %>%
 visGroups(groupname = "B", shape = "icon", 
           icon = list(code = "f007", color = "red")) %>%
 addFontAwesome() %>%
 visLegend(addNodes = list(
  list(label = "Group", shape = "icon", 
       icon = list(code = "f0c0", size = 25)),
  list(label = "User", shape = "icon", 
       icon = list(code = "f007", size = 50, color = "red"))), 
  useGroups = FALSE)

# # using a data.frame
# addNodes <- data.frame(label = c("Group", "User"), shape = "icon",
#  icon.code = c("f0c0", "f007"), icon.size = c(25, 50), icon.color = c(NA, "red"))
# 
# visNetwork(nodes, edges) %>%
#  visGroups(groupname = "A", shape = "icon", icon = list(code = "f0c0", size = 75)) %>%
#  visGroups(groupname = "B", shape = "icon", icon = list(code = "f007", color = "red")) %>%
#  addFontAwesome() %>%
#  visLegend(addNodes = addNodes,
#    addEdges = data.frame(label = "link"), useGroups = FALSE)
```