---
pagetitle: Nodes
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### We can customize nodes with a lot of options, and by various ways. 

## Individual configuration

As seen in the introduction, *nodes* must be a data.frame, with at least one column ```id```. You can add properties simply by adding variables on data.frame. See **?visNodes** for available options. 

The most used are presented in the following example :

```{r}
nodes <- data.frame(id = 1:10,
                    
  # add labels on nodes
  label = paste("Node", 1:10),
  
  # add groups on nodes 
  group = c("GrA", "GrB"),
  
  # size adding value
  value = 1:10,          
  
  # control shape of nodes
  shape = c("square", "triangle", "box", "circle", "dot", "star",
  "ellipse", "database", "text", "diamond"),
  
  # tooltip (html or character), when the mouse is above
  title = paste0("<p><b>", 1:10,"</b><br>Node !</p>"),
  
  # color
  color = c("darkred", "grey", "orange", "darkblue", "purple"),
  
  # shadow
  shadow = c(FALSE, TRUE, FALSE, TRUE, TRUE))             

# head(nodes)
# id  label group value    shape                     title    color shadow
#  1 Node 1   GrA     1   square <p><b>1</b><br>Node !</p>  darkred  FALSE
#  2 Node 2   GrB     2 triangle <p><b>2</b><br>Node !</p>     grey   TRUE

edges <- data.frame(from = c(1,2,5,7,8,10), to = c(9,3,1,6,4,7))
```

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%")
```

## Global configuration

If you want to set some configuration for all nodes, it's possible in a simpler way, using the **visNodes** function directly :

```{r}
nodes <- data.frame(id = 1:4)
edges <- data.frame(from = c(2,4,3,3), to = c(1,2,4,2))

visNetwork(nodes, edges, width = "100%") %>% 
  visNodes(shape = "square", 
           color = list(background = "lightblue", 
                        border = "darkblue",
                        highlight = "yellow"),
           shadow = list(enabled = TRUE, size = 10)) %>%
  visLayout(randomSeed = 12) # to have always the same network         
```

Finally, you can also combine individual and global options : 

```{r}
nodes <- data.frame(id = 1:4, 
                    shape = c("circle", "square"), 
                    label = LETTERS[1:4])
edges <- data.frame(from = c(2,4,3,3), to = c(1,2,4,2))

visNetwork(nodes, edges, width = "100%") %>% 
  visNodes(color = list(background = "lightblue", 
                        border = "darkblue",
                        highlight = "yellow"),
           shadow = list(enabled = TRUE, size = 10))  %>%
  visLayout(randomSeed = 12) # to have always the same network                     
```

## Use complex configuration individually

Available since __visNetwork_0.2.1__. When options are available using a list, you can use it in a data.frame with specific notation like this (a dot per level): 


```{r}
nodes <- data.frame(id = 1:3, 
                    color.background = c("red", "blue", "green"),
                    color.highlight.background = c("red", NA, "red"), 
                    shadow.size = c(5, 10, 15))

edges <- data.frame(from = c(1,2), to = c(1,3),
                    label = LETTERS[1:2], 
                    font.color =c ("red", "blue"), 
                    font.size = c(10,20))

visNetwork(nodes, edges)  
```