---
pagetitle: Options
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

Some options are available using **visOptions()**.

```{r, echo=TRUE}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = c(8,2,7,6,1,8,9,4,6,2),
 to = c(3,7,2,7,9,1,5,3,2,9),
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```


## Highlight nearest

You can highlight nearest nodes and edges clicking on a node with ````highlightNearest````.
Just click everywhere except on nodes to reset network : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE) %>%
  visLayout(randomSeed = 123)
```

It's now possible to control the ````degree```` of depth (visNetwork >= 0.1.2) : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = list(enabled =TRUE, degree = 2)) %>%
  visLayout(randomSeed = 123)
```


## Select by node id

You can also select a node by id/label with a list  with ````nodesIdSelection```` : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visLayout(randomSeed = 123)
```

## Select by a column

New feature in __visNetwork_0.1.2__ : select subset of nodes by the values of a column using ````selectedBy```` :

```{r}
# on "authorised" column
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = "group") %>%
  visLayout(randomSeed = 123)
```

```{r}
# or new column
nodes$sample <- sample(c("sample 1", "sample 2"), nrow(nodes), replace = TRUE)
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = "sample") %>%
  visLayout(randomSeed = 123)
```

## Data Manipulation

Using ````manipulation````, you can edit your network : 

* Add/delete nodes/edges
* Change links

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(manipulation = TRUE) %>%
  visLayout(randomSeed = 123)
```

## "Les miserables" example

```{r}
nodes <- jsonlite::fromJSON("https://raw.githubusercontent.com/DataKnowledge/DataKnowledge.github.io/master/visNetwork/data/nodes_miserables.json")

edges <- jsonlite::fromJSON("https://raw.githubusercontent.com/DataKnowledge/DataKnowledge.github.io/master/visNetwork/data/edges_miserables.json")


visNetwork(nodes, edges, height = "700px", width = "100%") %>%
  visOptions(selectedBy = "group", highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visPhysics(stabilization = FALSE)
```