---
pagetitle: Options
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

Some options are available using *visOptions()*.

```{r, echo=TRUE}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = trunc(runif(nb)*(nb-1))+1,
 to = trunc(runif(nb)*(nb-1))+1,
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```


## Highlight nearest

You can highlight nearest nodes and edges clicking on a node with **highlightNearest** option :

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE)
```

It's now possible to control the degree of depth (visNetwork >= 0.1.2) : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = list(enabled =TRUE, degree = 2))
```


## Select by node id
You can also select nodes by id/label with a list  with **nodesIdSelection** : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)
```

## Select by a column

New feature in __visNetwork_0.1.2__ : select some nodes by the values of a column using **selectedBy** option :

```{r}
# on "authorised" column
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
 visOptions(selectedBy = "group")
```

```{r}
# or new column
nodes$sel <- sample(c("sel1", "sel2"), nrow(nodes), replace = TRUE)
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
 visOptions(selectedBy = "sel")
```

## Data Manipulation
And some data manipulation tools :

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(manipulation = TRUE)
```

## "Les misérables" example


```{r}
nodes <- jsonlite::fromJSON("https://raw.githubusercontent.com/DataKnowledge/DataKnowledge.github.io/master/visNetwork/data/nodes_miserables.json")

edges <- jsonlite::fromJSON("https://raw.githubusercontent.com/DataKnowledge/DataKnowledge.github.io/master/visNetwork/data/edges_miserables.json")


visNetwork(nodes, edges, height = "600px", width = "100%")
```