---
pagetitle: Options
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### Some custom options are available using **visOptions()**.

```{r, echo=TRUE}
# data used in next examples
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = c(8,2,7,6,1,8,9,4,6,2),
 to = c(3,7,2,7,9,1,5,3,2,9),
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))
```


## Highlight nearest

You can highlight nearest nodes and edges clicking on a node with ````highlightNearest````.
Just click everywhere except on nodes to reset network : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE) %>%
  visLayout(randomSeed = 123)
```

It's now possible to control the ````degree```` of depth (**fix/improve performance in 1.0.0**), and to enable this options also hovering nodes (``hover``, **>=1.0.0**). Using ``hover``, you can still use ``click`` to set a view :

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = list(enabled = T, degree = 2, hover = T)) %>%
  visLayout(randomSeed = 123)
```

Since __visNetwork_1.0.0__, its now possible to use this feature with __images__ and __icons__ :

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visGroups(groupname = "A", shape = "icon", 
            icon = list(code = "f0c0", size = 75)) %>%
  visGroups(groupname = "B", shape = "icon", 
            icon = list(code = "f007", color = "red")) %>%
  visGroups(groupname = "C", shape = "icon", 
            icon = list(code = "f1b9", color = "black")) %>%
  visOptions(highlightNearest = list(enabled =TRUE, degree = 2, hover = T)) %>%
  addFontAwesome() %>%
  visLayout(randomSeed = 123)
```



## Select by node id

You can also select a node by id/label with a list using ````nodesIdSelection```` : 

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visLayout(randomSeed = 123)
```

## Select by a column

Since __visNetwork_0.1.2__ : select subset of nodes by the values of a column using ````selectedBy````, and node can have mutliple groups since __visNetwork_0.2.2__ :

```{r}
# on "authorised" column
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = "group") %>%
  visLayout(randomSeed = 123)
```

```{r}
# or new column, with multiple groups
nodes$sample <- paste(sample(LETTERS[1:3], nrow(nodes), replace = TRUE),
                      sample(LETTERS[1:3], nrow(nodes), replace = TRUE), 
                      sep = ",")
nodes$label <- nodes$sample # for see groups

visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = list(variable = "sample", multiple = T)) %>%
  visLayout(randomSeed = 123)
```

## Customize options

New features are available in __visNetwork_0.2.0__ for customize ````selectedBy```` & ````nodesIdSelection```` : 

* ````values```` : control the available values in the list
* ````selected```` : initialize a selection
* ````style```` : customize __css__ of list

This is an example on ````nodesIdSelection```` :

```{r, echo = FALSE}
nodes$label = paste("Label", 1:nb)
```

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(highlightNearest = TRUE, 
              nodesIdSelection = list(enabled = TRUE,
                                 selected = "8",
                                 values = c(5:10),
                                 style = 'width: 200px; height: 26px;
                                 background: #f8f8f8;
                                 color: darkblue;
                                 border:none;
                                 outline:none;')) %>%
  visLayout(randomSeed = 123)
```


## Data Manipulation

Using ````manipulation````, you can edit your network : 

* Add/delete nodes/edges
* Change links

```{r}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visOptions(manipulation = TRUE) %>%
  visLayout(randomSeed = 123)
```

## "Les miserables" example

```{r}
nodes <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/nodes_miserables.json")

edges <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/edges_miserables.json")


visNetwork(nodes, edges, height = "700px", width = "100%") %>%
  visOptions(selectedBy = "group", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visPhysics(stabilization = FALSE)
```