---
pagetitle: Performance
---

```{r, eval=TRUE, echo = FALSE}
require("visNetwork", quietly = TRUE)
```

### With default/some options, render network can be long. Here are some ways to improve the performance : 

* By default, and if we don't pass any information about coordinates, [vis.js](http://visjs.org/) computes coordinates dynamically and wait for stabilization before rendering. You can disable or control stabilization using ``visPhysics`` : 

```{r, eval = FALSE}
visNetwork(nodes, edges) %>%
  visPhysics(stabilization = FALSE)
```

* Another tips is to disabled smooth curve for edges. It's better for performance :

```{r, eval = FALSE}
visNetwork(nodes, edges) %>%
  visEdges(smooth = FALSE)
```

* Since __visNetwork_0.2.1__, it's possible to make the link between the features of package [igraph](http://igraph.org/r/) and those of __visNetwork__. The best way to increace plotting time is actually to use [igraph](http://igraph.org/r/) layout to compute coordinates before with ``visIgraphLayout()`` :

```{r, eval = FALSE}
visNetwork(nodes, edges) %>%
  visIgraphLayout()
```