---
pagetitle: rAmCharts - amBoxplot
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amBoxplot</h1>

## Parameters

* __object__: a vector, data.frame, a matrix, or a formula.
* __data__: a data.frame, from which the variables in formula should be taken.
* __use.cols__: a logical, for matrix only. Set to TRUE to display boxplot based on columns.
* __xlab__: a character, label for x-axis.
* __ylab__: a character, label for y-axis.
* __ylim__: a numeric, y values range with sensible defaults.
* __names__: a character, name on x-axis, if object is a vector.
* __col__: a character, color(s) to be used to fill the boxplot.
* __horiz__: a boolean, TRUE for an horizontal chart, FALSE for a vertical one.
* __id__: a character, column name of id to identify outliers, if object is a dataframe.
* __...__: other parameters called in amOptions. 


## Basic example - formula
```{r}
dataset <- get(x = "ChickWeight", pos = "package:datasets")
amBoxplot(weight~Diet, data=dataset)
```

## Basic example - dataframe
```{r}
don <- data.frame(a = 1:10, b = 1:5)
amBoxplot(don, ylim = c(0,15))
```

## Basic example - matrix
```{r}
mat <- matrix(nrow = 10, ncol = 5, rnorm(50))
amBoxplot(mat)
```

## Basic example - vector
```{r}
amBoxplot(rnorm(100))
```

## Horizontal boxplot
```{r}
amBoxplot(weight~Diet, data=dataset, horiz = TRUE)
```

## Display boxplot absed on matrix's rows
```{r}
mat <- matrix(nrow = 10, ncol = 5, rnorm(50))
amBoxplot(mat, use.cols = FALSE)
```

## Naming axis
```{r}
amBoxplot(weight~Diet, data=dataset, xlab = "diet", ylab = "weight")
```

## Y limits 
```{r}
amBoxplot(weight~Diet, data=dataset, ylim = c(0, 100))
```

## Change color
```{r}
amBoxplot(weight~Diet, data=dataset, col = "#CD1076")
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, export = TRUE)
#or
amBoxplot(weight~Diet, data=dataset, labelRotation = -45) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, export = TRUE)
```
  
## exportFormat
```{r, echo = TRUE, eval = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, export = TRUE,
          exportFormat = "JPG")
#or
amBoxplot(weight~Diet, data=dataset, labelRotation = -45) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, export = TRUE, 
          exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, main = "My Barchart",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
#or
amBoxplot(weight~Diet, data=dataset, labelRotation = -45) %>>% 
  amOptions( main = "My Barchart",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amBoxplot(weight~Diet, data=dataset, labelRotation = -45, 
       main = "My Barchart",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amBoxplot(weight~Diet, data=dataset, 
          theme = "dark")
#or
amBoxplot(weight~Diet, data=dataset) %>>% 
  amOptions(theme = "dark")
```
```{r, echo = FALSE}
amBoxplot(weight~Diet, data=dataset, theme = "dark")
```
