---
pagetitle: rAmCharts - amBullet
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amBullet</h1>

## Parameters

* __value__: a numeric
* __min__: a numeric, minimum value allowed.
* __max__: a numeric, maximum value allowed.
* __val_color__: a character, color of the bar value, in hexadecimal.
* __limit__: a numeric, target value.
* __limit_color__: a character, color of the line limit, in hexadecimal.
* __rates__: a data frame with 4 columns : name (character), min (numeric), max (numeric), and color (character, color in hexadecimal).
* __steps__: a boolean.
* __label__: a character, label of the bullet.
* __horiz__: a boolean, TRUE (default) for an horizontal bullet chart, FALSE for a vertical one.
* __...__: other parameters called in amOptions.


## Reference example

```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65)
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65) %>>% plot(height = "150px", width = "60%")
```

## Remove steps from backgroud
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, steps = FALSE)
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65, steps = FALSE) %>>% plot(height = "150px", width = "60%")
```

## Tune the colors
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, val_color = "purple", limit_color = "#3c8dbc")
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65, val_color = "purple", limit_color = "#3c8dbc") %>>% plot(height = "150px", width = "60%")
```

## Change orientation
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, horiz = FALSE)
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65, horiz = FALSE) %>>% plot(height = "500px", width = "150px")
```

## Add label
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, label = "Evaluation")
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65, label = "Evaluation") %>>% plot(height = "150px", width = "70%")
```

## Change mon and max
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, min = 20, max = 90)
```
```{r, echo = FALSE, eval = TRUE}
amBullet(value = 65, min = 20, max = 90) %>>% plot(height = "150px", width = "60%")
```


<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, export = TRUE)
#or
amBullet(value = 65) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amBullet(value = 65, export = TRUE) %>>% plot(height = "150px", width = "60%")
```

## exportFormat 
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, export = TRUE, exportFormat = "JPG")
#or
amBullet(value = 65) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amBullet(value = 65, export = TRUE, exportFormat = "JPG") %>>% plot(height = "150px", width = "60%")
```

## main and creditsPosition</h2>
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, main = "My Bullet",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
#or
amBullet(value = 65) %>>% 
  amOptions( main = "My Bullet",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amBullet(value = 65,  main = "My Bullet", mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right") %>>%
  plot(height = "200px", width = "60%")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amBullet(value = 65, main = "My Bullet", theme = "patterns")
#or
amBullet(value = 65) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amBullet(value = 65, theme = "patterns") %>>% plot(height = "150px", width = "60%")
```
