---
pagetitle: rAmCharts - amCandlestick
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amCandlestick</h1>

## Parameters

* __data__: a dataframe with at least 5 columns: category, open (numeric), close (numeric), low (numeric), high (numeric). 
* __dataDateFormat__: a character, default 'NULL'. Even if your chart parses dates, you can pass them as strings in your data - all you need to do is to set data date format and the chart will parse dates to date objects. Please note that two-digit years (YY) as well as literal month names (MMM)  are NOT supported in this setting.
* __minPeriod__: a character. minPeriod Specifies the shortest period of your data. This should be set only if dataDateFormat is not 'NULL'. Possible period values: fff - milliseconds, ss - seconds, mm - minutes, hh - hours, DD - days, MM - months, YYYY - years. It's also possible to supply a number for increments, i.e. '15mm' which will instruct the chart that your data is supplied in 15 minutes increments.
* __positiveColor__: a character, color for positive values. Must be in hexadecimal if you plan to export the chart.
* __negativeColor__: a character, color for negative values. Must be in hexadecimal if you plan to export the chart.
* __names__: a character, names for the tooltips.
* __xlab__: a character, label for x-axis.
* __ylab__: a character, label for y-axis.
* __horiz__: a boolean, TRUE for an horizontal chart, FALSE for a vertical one.
* __...__: other parameters called in amOptions. 

Data used in the examples:
```{r}
data("data_candleStick2")
head(data_candleStick2)
```

## Reference example

```{r}
amCandlestick(data = data_candleStick2, labelRotation = -45)
```

## Change colors
```{r}
amCandlestick(data = data_candleStick2, positiveColor = "black", negativeColor = "green", 
              labelRotation = -45)
```

## Naming axis
```{r}
amCandlestick(data = data_candleStick2, ylab = "values", 
              labelRotation = -45)
```

## Rotate x axis labels
```{r}
amCandlestick(data = data_candleStick2, labelRotation = 90)
```

## Change names
```{r}
amCandlestick(data = data_candleStick2, names = c("min", "begin", "end", "max"), 
              labelRotation = -45)
```

## Horizontal chart
```{r}
amCandlestick(data = data_candleStick2, horiz = TRUE)
```

## Parse dates
```{r}
amCandlestick(data = data_candleStick2, dataDateFormat = "YYYY-MM-DD", 
              labelRotation = -45)
```

## Data over months
```{r}
data_candleStick2$category <- c("2015-01-01", "2015-02-01", "2015-03-01",
                                "2015-04-01", "2015-05-01", "2015-06-01",
                                "2015-07-01", "2015-08-01", "2015-09-01",
                                "2015-10-01", "2015-11-01", "2015-12-01")

amCandlestick(data = data_candleStick2, dataDateFormat = "YYYY-MM-DD", minPeriod = "MM", 
              labelRotation = -45)
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amCandlestick(data = data_candleStick2, export = TRUE, labelRotation = -45)
#or
amCandlestick(data = data_candleStick2, labelRotation = -45) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amCandlestick(data = data_candleStick2, export = TRUE, labelRotation = -45)
```
  
## exportFormat
```{r, echo = TRUE, eval = FALSE}
amCandlestick(data = data_candleStick2, export = TRUE, exportFormat = "JPG", 
              labelRotation = -45)
#or
amCandlestick(data = data_candleStick2, labelRotation = -45) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amCandlestick(data = data_candleStick2, export = TRUE, exportFormat = "JPG", 
              labelRotation = -45)
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amCandlestick(data = data_candleStick2, main = "My Candlestick",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right", 
        labelRotation = -45)
#or
amCandlestick(data = data_candleStick2, labelRotation = -45) %>>% 
  amOptions( main = "My Candlestick",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amCandlestick(data = data_candleStick2, 
       main = "My Candlestick",
       mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right",
       labelRotation = -45)
```

<h2 class="partdivtitle">theme</h2>
```{r, echo = TRUE, eval = FALSE}
amCandlestick(data = data_candleStick2, theme = "patterns",
              labelRotation = -45)
#or
amCandlestick(data = data_candleStick2, labelRotation = -45) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amCandlestick(data = data_candleStick2, theme = "patterns", labelRotation = -45)
```
