---
pagetitle: rAmCharts - amFunnel
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amFunnel</h1>

## Parameters

* __data__: a dataframe with at least 2 columns: value (numeric, positive), and description (character). See data_funnel for example. You can add a third column "color" (character, colors in hexadecimal) to specify the colors.
* __neck_height__: a numeric, value between 0 and 100 : if a bottleneck is desired, this value determines its heigh. Default to NULL.
* __neck_width__: a numeric, value between 0 and 100 : if a bottleneck is desired, this value determines its width. Default to NULL.
* __depth__: a numeric, between 0 and 100. If superior to 0, chart is displayed in 3D. Only for pyramid chart (without a bottleneck). 
* __inverse__: a boolean, if TRUE, the funnel chart will be inversed. 
* __label_side__: a character, defines the label position : "right" or "left". 
* __margin_right__: a numeric, margin at the right side.
* __margin_left__: a numeric, margin at the left side.
* __...__: other parameters called in amOptions.


Data used in the examples:
```{r}
data("data_funnel")
head(data_funnel)
```

## Reference example : Pyramid chart

```{r}
amFunnel(data = data_funnel, inverse = TRUE)
```

## Reference example : Funnel chart
```{r}
amFunnel(data = data_funnel, neck_height = 30, neck_width = 40)
```

## Inversed Pyramid chart 
```{r}
amFunnel(data = data_funnel, inverse = FALSE)
```

## Change label side
```{r}
amFunnel(data = data_funnel, inverse = FALSE, label_side = "left")
```

## 3D pyramid
```{r}
amFunnel(data = data_funnel, depth = 50, inverse = TRUE)
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, export = TRUE)
#or
amFunnel(data = data_funnel, inverse = FALSE) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, export = TRUE)
```

## exportFormat
```{r, echo = TRUE, eval = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, export = TRUE, exportFormat = "JPG")
#or
amFunnel(data = data_funnel, inverse = FALSE) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, export = TRUE, exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, main = "My Pyramid",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
#or
amFunnel(data = data_funnel, inverse = FALSE) %>>% 
  amOptions( main = "My Pyramid",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
```
```{r, echo = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, 
       main = "My Pyramid",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, theme = "patterns")
#or
amFunnel(data = data_funnel, inverse = FALSE) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amFunnel(data = data_funnel, inverse = FALSE, theme = "patterns")
```
