---
pagetitle: rAmCharts - amHist
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

## Parameters

* __x__: a vector of values for which the histogram is desired.
* __col__: a colour to be used to fill the bars.
* __border__: a colour for the borders.
* __freq__: logical if TRUE, the histogram graphic is a representation of frequencies, the counts component of the result; if FALSE, probability densities, component density, are plotted (so that the histogram has a total area of one). Defaults to TRUE if and only if breaks are equidistant (and probability is not specified).
* __labels__: logical or character. Additionally draw labels on top of bars, if not FALSE; if TRUE, draw the counts or rounded densities; if labels is a character, draw itself.
* __xlab, ylab__: character, labels of the axis.
* __ylim__: the range of y values with sensible defaults.
* __control_hist__: (optional) named list containing parameters for computing the histogram.
* __...__: other parameters called in amOptions.

Data used in the examples:
```{r}
data_hist <- get(x = "iris", pos = "package:datasets")$Sepal.Length
head(data_hist)
```

## Reference example

```{r}
amHist(x = data_hist)
```

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Filling color </h2>
```{r}
amHist(x = data_hist, col = "#367fa9")
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Border color </h2>
```{r}
amHist(x = data_hist, border = "#367fa9")
```
  </div>
</div>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> View frequency </h2>
```{r}
amHist(x = data_hist, freq = FALSE)
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Labels </h2>
```{r}
amHist(x = data_hist, xlab = "xlab", ylab = "ylab")
```
  </div>
</div>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Add label on the top </h2>
```{r}
amHist(x = data_hist, labels = TRUE)
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Set ylim </h2>
```{r}
amHist(x = data_hist, ylim = c(0,.8), freq = FALSE)
```
  </div>
</div>
