---
pagetitle: rAmCharts - amHist
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

# rAmCharts - amHist

## Parameters

* __x__: a vector of values for which the histogram is desired.
* __col__: a colour to be used to fill the bars.
* __border__: a colour for the borders.
* __freq__: logical if TRUE, the histogram graphic is a representation of frequencies, the counts component of the result; if FALSE, probability densities, component density, are plotted (so that the histogram has a total area of one). Defaults to TRUE if and only if breaks are equidistant (and probability is not specified).
* __labels__: logical or character. Additionally draw labels on top of bars, if not FALSE; if TRUE, draw the counts or rounded densities; if labels is a character, draw itself.
* __xlab, ylab__: character, labels of the axis.
* __ylim__: the range of y values with sensible defaults.
* __control_hist__: (optional) named list containing parameters for computing the histogram.
* __...__: other parameters called in amOptions.

Data used in the examples:
```{r}
data_hist <- get(x = "iris", pos = "package:datasets")$Sepal.Length
head(data_hist)
```

## Reference example

```{r}
amHist(x = data_hist)
```

## Filling color
```{r}
amHist(x = data_hist, col = "#CECECE")
```

## Border color
```{r}
amHist(x = data_hist, border = "#CECECE")
```

## View frequency
```{r}
amHist(x = data_hist, freq = FALSE)
```

## Labels
```{r}
amHist(x = data_hist, xlab = "xlab", ylab = "ylab")
```

## Add label on the top
```{r}
amHist(x = data_hist, labels = TRUE)
```

## Set ylim
```{r}
amHist(x = data_hist, ylim = c(0,.8), freq = FALSE)
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amHist(x = data_hist, export = TRUE)
#or
amHist(x = data_hist) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amHist(x = data_hist, export = TRUE)
```
  
## exportFormat
```{r, echo = TRUE, eval = FALSE}
amHist(x = data_hist, export = TRUE, exportFormat = "JPG")
#or
amHist(x = data_hist) %>>% 
  amOptions(export = TRUE, exportFormat = "CSV")
```
```{r, echo = FALSE}
amHist(x = data_hist, export = TRUE, exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amHist(x = data_hist, main = "My Histogram",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
#or
amHist(x = data_hist) %>>% 
  amOptions( main = "My Histogram",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amHist(x = data_hist, 
       main = "My Histogram",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amHist(x = data_hist, theme = "patterns")
#or
amHist(x = data_hist) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amHist(x = data_hist, theme = "patterns")
```

