---
pagetitle: rAmCharts - amMekko
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amMekko</h1>

## Parameters

* __x__: a character, column name for x-axis.
* __y__: a character, column name for y-axis.
* __data__: a dataframe with values to display. See data_mekko for example.
* __groups_color__: character, a vector of colors in hexadecimal, same length as the number of y modalities.
* __xlab__: a character, label for x-axis.
* __ylab__: a character, label for y-axis.
* __horiz__: a boolean, TRUE for an horizontal chart, FALSE for a vertical one.
* __show_values__: a boolean, TRUE to display values.
* __...__: other parameters called in amOptions.


Data used in the examples:
```{r}
data("data_mekko")
head(data_mekko)
```

## Reference example

```{r}
amMekko(x = "var1", y = "var2", data = data_mekko)
```

## Horizontal chart
```{r}
amMekko(x = "var1", y = "var2", data = data_mekko, horiz = TRUE)
```

## Display values
```{r}
amMekko(x = "var1", y = "var2", data = data_mekko, show_values = TRUE)
```


<h2 class="partdivtitle">amOptions</h2>

## legend
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, legend = TRUE)
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, legend = TRUE)
```

## legendPosition
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, legend = TRUE, legendPosition = "left")
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions(legend = TRUE, legendPosition = "left")
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, legend = TRUE, legendPosition = "left")
```

## export
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, export = TRUE)
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, export = TRUE)
```

## exportFormat
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, export = TRUE, exportFormat = "JPG")
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, export = TRUE, exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, main = "My Mekko",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions( main = "My Mekko",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, 
       main = "My Mekko",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-left")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, theme = "patterns")
#or
amMekko(x = "var1", y = "var2", data = data_mekko) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amMekko(x = "var1", y = "var2", data = data_mekko, theme = "patterns")
```
