---
pagetitle: rAmCharts - amPie
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

## Parameters

* __data__: a dataframe with at least 2 columns: label (character), and value (numeric). See data_pie for example. You can add a third column "color" (character, colors in hexadecimal) to specify the colors.
* __show_values__: a boolean, TRUE to display values.
* __depth__: a numeric, between 0 and 100. If superior to 0, chart is displayed in 3D. 
* __inner_radius__: a numeric, between 0 ans 100. If superior to 0, the pie becomes a donut chart. 
* __...__: other parameters called in amOptions.

Data used in the examples:
```{r}
data("data_pie")
head(data_pie)
```

## Reference example

```{r}
amPie(data = data_pie)
```

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Don't display values </h2>
```{r}
amPie(data = data_pie, show_values = FALSE)
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> 3D pie </h2>
```{r}
amPie(data = data_pie, depth = 10)
```
  </div>
</div>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Donut chart </h2>
```{r}
amPie(data = data_pie, inner_radius = 50)
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> All options </h2>
```{r}
amPie(data = data_pie, inner_radius = 50, depth = 10, show_values = TRUE)
```
  </div>
</div>

<h2 class="amOptions">amOptions</h2>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">legend</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, legend = TRUE)
#or
amPie(data = data_pie) %>>% amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amPie(data = data_pie, legend = TRUE)
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">legendPosition</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, legend = TRUE, legendPosition = "left")
#or
amPie(data = data_pie) %>>% amOptions(legend = TRUE, legendPosition = "left")
```
```{r, echo = FALSE}
amPie(data = data_pie, legend = TRUE, legendPosition = "left")
```
  </div>
</div>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">export</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, export = TRUE)
#or
amPie(data = data_pie) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amPie(data = data_pie, export = TRUE)
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">exportFormat</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, export = TRUE, exportFormat = "CSV")
#or
amPie(data = data_pie) %>>% 
  amOptions(export = TRUE, exportFormat = "CSV")
```
```{r, echo = FALSE}
amPie(data = data_pie, export = TRUE, exportFormat = "CSV")
```
  </div>
</div>



<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">main and creditsPosition</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, main = "My Pie",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
#or
amPie(data = data_pie) %>>% 
  amOptions( main = "My Pie",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amPie(data = data_pie, 
       main = "My Pie",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">theme</h2>
```{r, echo = TRUE, eval = FALSE}
amPie(data = data_pie, main = "My Pie", theme = "patterns")
#or
amPie(data = data_pie) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amPie(data = data_pie, theme = "patterns")
```
  </div>
</div>

