---
pagetitle: rAmCharts - amPlot
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```


<h1>rAmCharts - amPlot</h1>

## Parameters
  
* __x__:  numeric, data.frame, or formula, the coordinates of points in the plot.
* __y__:  numeric, the y coordinates of points in the plot, optional if x is an appropriate structure.
* __bullet__: character, point shape. Possible values are : "diamond", "square", "bubble", "yError", "xError", "round", "triangleLeft", "triangleRight", "triangleUp", "triangleDown". Default set to "round".
* __type__: character, type of plot. Possible values are : "l" for a line, "sl" for a smoothed line, "st" for steps, "p" for points, and "b" for line and points. Default set to "p".
* __col__: either a factor or a character, default set to "gray".
* __weights__: numeric, weights for x/y charts only. Default set to rep(1, x).
* __precision__: numeric, precision you wish to display. Default set to 2.
* __id__: numeric, point id, for x/y charts only. Default 1:length(x).
* __error__: numeric, only when type is "xError" "yError" default NULL,
* __xlab__: character, label for x-axis.
* __ylab__: character, label for y-axis.
* __lty__: numeric, line type (dashes).
* __cex__: numeric, bullet size.
* __lwd__: numeric, line width.
* __xlim__: numeric, x range.
* __ylim__: numeric, y range.
* __parseDates__: logical, default set to FALSE, if TRUE argument dataDateFormat has to be provided.
* __dataDateFormat__: character, default set to NULL. Even if your chart parses dates, you can pass them as strings in your dataframe - all you need to do is to set data date format and the chart will parse dates to date objects. Check this page for available formats. Please note that two-digit years (YY) as well as literal month names (MMM) are NOT supported in this setting.
* __columns__: (optional) either a vector of character containing the names of the series to draw, or a numeric vector of indices. By default all numeric columns will be drawn.
* __data__: dataset
* __...__: other parameters called in amOptions.


## Scatter plot
```{r}
xc <- paste("cat.", 1:100)
y <- rnorm(length(xc))
```

```{r}
amPlot(x = xc, y = y)
```

## Line and other types
```{r}
amPlot(x = xc, y = y, type = "b") # can also be "l", "sl"
```

```{r}
amPlot(x = xc, y = y, type = "st")
```

## XY chart with optional weights (iif when x is numeric)
```{r}
x <- sort(rnorm(100))
```

```{r, eval = TRUE}
amPlot(x = x, y = y, weights = runif(100, 4, 7), col="#663300")
```

## Change type
```{r, eval = TRUE}
amPlot(x = xc, y = y, type = 'l')
```

## Add a legend

```{r}
amPlot(x = x, y = y, type = "l", legend = TRUE)
```

## Add a scrollbar, lty and cex

```{r}
amPlot(x = x, y = y, scrollbar = TRUE, lty = 2,  type = "l")
```

## Change color, main
```{r, echo = TRUE, eval = FALSE}
amPlot(x = x, y = y, col = "blue", main = "title")
```
```{r, echo = FALSE, eval = TRUE}
amPlot(x = x, y = y, col = "blue", main = "title")
```

## Select the column
```{r, echo = TRUE, eval = FALSE}
amPlot(iris, col = colnames(iris)[1:2], type = c("l", "st"))
```
```{r, echo = FALSE, eval = TRUE}
amPlot(iris, col = colnames(iris)[1:2], type = c("l", "st"))
```
