---
  pagetitle: amRadar
---

<div class="partdivtitle">
# amRadar
</div>
  <br>
  <div class="partdivtitle">
## settings
</div>
  
<ul>
<li> data : data.frame first column is named "label" (character), other columns are series of values</li>
<li> col  : character, color(s) of serie(s) hexadecimal like "#00FF00"
<li> backTransparency : numeric,  background transparency, between 0 and 1
<li> type : character,  type of radar, must be "polygons" or "circle"
<li> pch : character, symbols must be in "round", "square", "triangleUp",  "triangleDown", "triangleLeft", "triangleRight", "bubble","diamond", "xError", "yError" 
<li> ... : see amOptions for more options
</ul>

  ```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```
<div class="partdivtitle">
## Data use in example
</div>
```{r}
data <- data.frame(label = c("A", "Z", "E", "R", "T"),
                   Product1 = c(1, 2, 3, 4, 2), 
                   Product2 = c(2, 8, 1, 1, 0),
                   Product3 = c(1,1,2,2,4))
```


<div class="col2">
<div class="partdivtitle">
## Basic exemple
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data)
```
```{r, echo = FALSE}
amRadar(data) %>>% plot()
```
<div class="partdivtitle">
## Change color
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data, col = c("#0000FF", "#00FF00", "#FF0000"))
```
```{r, echo = FALSE}
amRadar(data, col = c("#0000FF", "#00FF00", "#FF0000")) %>>% plot()
```
</div>




<div class="partdivtitle">
## backTransparency
</div>
<br>
<div class="col2">
```{r, echo = TRUE, eval = FALSE}
amRadar(data, backTransparency = 1)
```
```{r, echo = FALSE}
amRadar(data, backTransparency = 1) %>>% plot()
```

```{r, echo = TRUE, eval = FALSE}
amRadar(data, backTransparency = c(0, 0.4, 0.6))
```
```{r, echo = FALSE}
amRadar(data, backTransparency = c(0, 0.4, 0.6)) %>>% plot()
```
</div>
<br>

<div class="partdivtitle">
## type
</div>
<br>
<div class="col2">

```{r, echo = TRUE, eval = FALSE}
amRadar(data, type = "circles")
```
```{r, echo = FALSE}
amRadar(data, type = "circles") %>>% plot()
```

```{r, echo = TRUE, eval = FALSE}
amRadar(data, type = "polygons") #default
```
```{r, echo = FALSE}
amRadar(data, type = "polygons") %>>% plot()#default
```
</div>

<div class="partdivtitle">
## pch
</div>
<div class="col4">

<br>


```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "triangleRight", backTransparency = 0)
```
```{r, echo = FALSE}
amRadar(data,  pch = "triangleRight", backTransparency = 0) %>>% plot()
```

<br>


```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "diamond", backTransparency = 0) 
```
```{r, echo = FALSE}
amRadar(data,  pch = "diamond", backTransparency = 0) %>>% plot()
```

<br>


```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "yError", backTransparency = 0)
```
```{r, echo = FALSE}
amRadar(data,  pch = "yError", backTransparency = 0)%>>% plot()
```

<br>


```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0)
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% plot()
```

</div>

<div class="amOption">
## amOptions
</div>
<div class="col2">
<div class="partdivtitle">
## legend
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, legend = TRUE)
#or
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, legend = TRUE) %>>% plot()
```

<div class="partdivtitle">
## legendPosition
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, legend = TRUE)
#or
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, legend = TRUE) %>>% plot()
```

</div>


<div class="col2">

<div class="partdivtitle">
## export
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, export = TRUE)
#or
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, 
        export = TRUE) %>>% plot()
```
<br>

<div class="partdivtitle">
## exportFormat
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, export = TRUE, exportFormat = "CSV")
#or
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions(export = TRUE, exportFormat = "CSV")
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, 
        export = TRUE, exportFormat = "CSV") %>>% plot()
```

</div>



<div class="col2">
<div class="partdivtitle">
## main and creditsPosition
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "bottom-right")
#or
amRadar(data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions( main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "bottom-right")
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 0, 
       main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right") %>>% plot()
```
<div class="partdivtitle">
## theme
</div>
<br>
```{r, echo = TRUE, eval = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 1, main = "My Radar", theme = "patterns")
#or
amRadar(data,  pch = "bubble", backTransparency = 1) %>>% 
  amOptions( theme = "patterns")
```
```{r, echo = FALSE}
amRadar(data,  pch = "bubble", backTransparency = 1, 
        theme = "patterns") %>>% plot()
```

</div>
