---
pagetitle: rAmCharts - amRadar
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

## Parameters
  

* __data__: data.frame first column is named "label" (character), other columns are series of values
* __col__: character, color(s) of serie(s) hexadecimal like "#00FF00"
* __backTransparency__: numeric,  background transparency, between 0 and 1
* __type__: character,  type of radar, must be "polygons" or "circle"
* __pch__: character, symbols must be in "round", "square", "triangleUp",  "triangleDown", "triangleLeft", "triangleRight", "bubble","diamond", "xError", "yError" 
* __...__: see amOptions for more options


## Data use in the following examples

```{r}
data <- data.frame(label = c("A", "Z", "E", "R", "T"),
                   Product1 = c(1, 2, 3, 4, 2), 
                   Product2 = c(2, 8, 1, 1, 0),
                   Product3 = c(1,1,2,2,4))
```

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle"> Basic exemple </h2>
```{r}
amRadar(data = data)
```
  </div>
  
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">Change color </h2>
```{r}
amRadar(data = data, col = c("#0000FF", "#00FF00", "#FF0000"))
```
  </div>
  
</div>

<h2 class="partdivtitle">backTransparency</h2>

<div class="row">
  <div class="col-xs-12 col-md-6">
```{r}
amRadar(data = data, backTransparency = 1)
```
  </div>
  <div class="col-xs-12 col-md-6">
```{r}
amRadar(data = data, backTransparency = c(0, 0.4, 0.6))
```
  </div>
</div>

<h2 class="partdivtitle">type</h2>

<div class="row">
  <div class="col-xs-12 col-md-6">
```{r}
amRadar(data = data, type = "circles")
```

  </div>
  <div class="col-xs-12 col-md-6">
```{r}
amRadar(data = data, type = "polygons") #default
```
  </div>
</div>

<h2 class="partdivtitle">pch</h2>
<div class="row">
  <div class="col-xs-12 col-md-3">
```{r}
amRadar(data = data,  pch = "triangleRight", backTransparency = 0)
```
  </div>
  
  <div class="col-xs-12 col-md-3">
```{r}
amRadar(data = data, pch = "diamond", backTransparency = 0) 
```
  </div>
  
  <div class="col-xs-12 col-md-3">
```{r}
amRadar(data = data,  pch = "yError", backTransparency = 0)
```
  </div>
  
  <div class="col-xs-12 col-md-3">
```{r}
amRadar(data = data,  pch = "bubble", backTransparency = 0)
```
  </div>
</div>

<h2 class="amOptions">amOptions</h2>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">legend</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, legend = TRUE)
#or
amRadar(data = data,  pch = "bubble", backTransparency = 0) %>>% amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, legend = TRUE)
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">legendPosition</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, legend = TRUE, legendPosition = "left")
#or
amRadar(data = data,  pch = "bubble", backTransparency = 0) %>>% amOptions(legend = TRUE, legendPosition = "left")
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, legend = TRUE, legendPosition = "left")
```
  </div>
</div>

<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">export</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, export = TRUE)
#or
amRadar(data = data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, 
        export = TRUE)
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">exportFormat</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, export = TRUE, exportFormat = "CSV")
#or
amRadar(data = data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions(export = TRUE, exportFormat = "CSV")
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, 
        export = TRUE, exportFormat = "CSV")
```
  </div>
</div>



<div class="row">
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">main and creditsPosition</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
#or
amRadar(data = data,  pch = "bubble", backTransparency = 0) %>>% 
  amOptions( main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 0, 
       main = "My Radar",
        mainColor = "#00FF00", mainSize = 25, creditsPosition = "top-right")
```
  </div>
  <div class="col-xs-12 col-md-6"><h2 class="partdivtitle">theme</h2>
```{r, echo = TRUE, eval = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 1, main = "My Radar", theme = "patterns")
#or
amRadar(data = data,  pch = "bubble", backTransparency = 1) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amRadar(data = data,  pch = "bubble", backTransparency = 1, theme = "patterns")
```
  </div>
</div>
