---
pagetitle: rAmCharts - amSolidGauge
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amSolidGauge</h1>

## Parameters

* __x__: numeric, equal to the value for which the solid gauge is desired.
* __min__: a numeric, minimum possible value.
* __max__: a numeric, maximum possible value. 
* __type__: a character, type of gauge : "full" or "semi".
* __width__: a numeric,  width of the gauge.
* __color__: a character, hexadecimal color value or a vector of colors. 
* __text__: a character, text to add to the printed value. 
* __textSize__: a numeric, size of text.
* __...__: other parameters called in amOptions.

## Reference example

```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65)
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65) %>>% plot(width = "40%")
```

## Change min and max values
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, min = 0, max = 200)
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, min = 0, max = 200) %>>% plot(width = "40%")
```

## Semi Solid Gauge
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, type = "semi")
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, type = "semi") %>>% plot(width = "40%")
```

## Change width
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, width = 50)
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, width = 50) %>>% plot(width = "40%")
```

## Change color
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, color = "#2F4F4F")
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, color = "#2F4F4F") %>>% plot(width = "40%")
```

## Put a color scale

```{r, echo = TRUE, eval = FALSE}
      amSolidGauge(x = 10, color = c("#00ff00", "#ffd700", "#ff0000"))
      amSolidGauge(x = 35, color = c("#00ff00", "#ffd700", "#ff0000"))
      amSolidGauge(x = 70, color = c("#00ff00", "#ffd700", "#ff0000"))
      amSolidGauge(x = 90, color = c("#00ff00", "#ffd700", "#ff0000"))
```

<div class="row">
  <div class="col-xs-12 col-md-6">
    ```{r, echo = FALSE, eval = TRUE}
      amSolidGauge(x = 10, color = c("#00ff00", "#ffd700", "#ff0000")) %>>% plot(width = "40%")
    ```
  </div>
  <div class="col-xs-12 col-md-6">
    ```{r, echo = FALSE, eval = TRUE}
      amSolidGauge(x = 35, color = c("#00ff00", "#ffd700", "#ff0000")) %>>% plot(width = "40%")
    ```
  </div>
</div>
<div class="row">
  <div class="col-xs-12 col-md-6">
    ```{r, echo = FALSE, eval = TRUE}
      amSolidGauge(x = 70, color = c("#00ff00", "#ffd700", "#ff0000")) %>>% plot(width = "40%")
    ```
  </div>
  <div class="col-xs-12 col-md-6">
    ```{r, echo = FALSE, eval = TRUE}
      amSolidGauge(x = 90, color = c("#00ff00", "#ffd700", "#ff0000")) %>>% plot(width = "40%")
    ```
  </div>
</div>

## Add some text to the printed value
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, text = "%")
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, text = "%") %>>% plot(width = "40%")
```

## Modify textSize value
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, text = "%", textSize = 50)
```
```{r, echo = FALSE, eval = TRUE}
amSolidGauge(x = 65, text = "%", textSize = 50) %>>% plot(width = "40%")
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, export = TRUE)
#or
amSolidGauge(x = 65) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amSolidGauge(x = 65, export = TRUE)  %>>% plot(width = "40%")
```

## exportFormat
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, export = TRUE, exportFormat = "JPG")
#or
amSolidGauge(x = 65) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amSolidGauge(x = 65, export = TRUE, exportFormat = "JPG")  %>>% plot(width = "40%")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amSolidGauge(x = 65, main = "My Gauge",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
#or
amSolidGauge(x = 65) %>>% 
  amOptions( main = "My Gauge",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amSolidGauge(x = 65, 
       main = "My Gauge",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")  %>>% plot(width = "40%")
```
