---
pagetitle: rAmCharts - amWaterfall
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amWaterfall</h1>

## Parameters

* __data__: a dataframe with at least 3 columns : label (character), value (numeric), operation (character : "plus", "minus", "total"). You can add a third column "color" (character, colors in hexadecimal). You can also add a column "description" (character) containing the text you want to display when mouse is on the graphic ('<br>' for a new line). See data_xaterfall for example.
* __start__: a numeric, value from which to start.
* __horiz__: a boolean, TRUE for an horizontal chart, FALSE for a vertical one.
* __show_values__: a boolean, TRUE ti dosplay values.
* __...__: other parameters called in amOptions. 

Data used in the examples:
```{r}
data("data_waterfall")
head(data_waterfall)
```

## Reference example

```{r}
amWaterfall(data = data_waterfall)
```

## Horizontal waterfall
```{r}
amWaterfall(data = data_waterfall, horiz = TRUE)
```

## Display values
```{r}
amWaterfall(data = data_waterfall, show_values = TRUE)
```

<h2 class="partdivtitle">amOptions</h2>

## export
```{r, echo = TRUE, eval = FALSE}
amWaterfall(data = data_waterfall, export = TRUE)
#or
amWaterfall(data = data_waterfall) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amWaterfall(data = data_waterfall, export = TRUE)
```
  
## exportFormat
```{r, echo = TRUE, eval = FALSE}
amWaterfall(data = data_waterfall, export = TRUE, exportFormat = "JPG")
#or
amWaterfall(data = data_waterfall) %>>% 
  amOptions(export = TRUE, exportFormat = "CSV")
```
```{r, echo = FALSE}
amWaterfall(data = data_waterfall, export = TRUE, 
          exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amWaterfall(data = data_waterfall, main = "My Waterfall",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
#or
amWaterfall(data = data_waterfall) %>>% 
  amOptions( main = "My Waterfall",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```
```{r, echo = FALSE}
amWaterfall(data = data_waterfall, 
       main = "My Waterfall",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "top-right")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amWaterfall(data = data_waterfall, theme = "patterns")
#or
amWaterfall(data = data_waterfall) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amWaterfall(data = data_waterfall, theme = "patterns")
```
