---
pagetitle: rAmCharts - amWind
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amWind</h1>

## Parameters
  

* __data__: data.frame columns are series of values from week wind(first column) to strong wind (last column), row are wind direction.
* __col__: character, color(s) of serie(s) hexadecimal like "#00FF00"
* __backTransparency__: numeric,  background transparency, between 0 and 1
* __...__: see amOptions for more options


```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

## Reference example

```{r}
 data("data_wind")
data_wind
```

## Basic exemple
```{r}
amWind(data = data_wind)
```

## Change color
```{r}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"))
```

## backTransparency
```{r}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), backTransparency = c(0.1, 0.2, 0.5))
```

<h2 class="partdivtitle">amOptions</h2>

## legend
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), legend = TRUE)
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"))%>>% 
  amOptions(legend = TRUE)
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), legend = TRUE)
```

## legendPosition
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), legend = TRUE,
        legendPosition = "left")
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF")) %>>% 
  amOptions(legend = TRUE, legendPosition = "left")
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), legend = TRUE,
        legendPosition = "left")
```

## export
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), export = TRUE)
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF")) %>>% 
  amOptions(export = TRUE)
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), export = TRUE)
```

## exportFormat
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), export = TRUE, exportFormat = "JPG")
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF")) %>>% 
  amOptions(export = TRUE, exportFormat = "JPG")
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), export = TRUE, exportFormat = "JPG")
```

## main and creditsPosition
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), main = "My Radar",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-right")
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF")) %>>% 
  amOptions( main = "My Radar",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-right")
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), main = "My Radar",
        mainColor = "#68838B", mainSize = 25, creditsPosition = "bottom-right")
```

## theme
```{r, echo = TRUE, eval = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), theme = "patterns")
#or
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF")) %>>% 
  amOptions(theme = "patterns")
```
```{r, echo = FALSE}
amWind(data = data_wind, col = c("#FF0000", "#00FF00", "#0000FF"), theme = "patterns")
```


