---
pagetitle: rAmCharts - amStockMultiSet
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

<h1>rAmCharts - amStockMultiSet</h1>


* __data__: a list, list of data.frame (same structure) first column is date, others are values.
* __panelColumn__: a numeric, control panel adding for selected series.
* __ZoomButton__: a data.frame, 3 columns : Unit, times unit. multiple : multiple*unit. label : button's label
* __color__: a character, color of series (in hexadecimal).
* __precision__: a numeric, digits precision.
* __export__: a logical, default set to FALSE. TRUE to display export feature.
* __percentHeightPanel__: a numeric, vector of size panel, same length than data.
* __creditsPosition__: a character, credits position. Possible values are : "top-right", "top-left", "bottom-right", "bottom-left".
* __...__: other first level attributes

## Reference example
```{r}
  data(data_stock_3)
  amStockMultiSet(data = data_stock_3)
``` 
  
## Multi pannels
```{r}
    data(data_stock_3)
    amStockMultiSet(data = data_stock_3, panelColumn = c(1,2,1,1))
``` 

## ZoomButton, export and pannel height
```{r}
 data(data_stock_3)
  ZoomButton <- data.frame(Unit = c('DD', 'DD', 'MAX'), multiple = c(10, 15 ,1),
                          label = c('10 days','15 days', 'MAX'))
  amStockMultiSet(data = data_stock_3, panelColumn = c(1,2,1,1), percentHeightPanel = c(3,1),
                  ZoomButtonPosition = 'left', ZoomButton = ZoomButton, export = TRUE, precision = 0)
``` 