---
pagetitle: Introduction
---

```{r,echo=FALSE, message=FALSE}
require(package = "rAmCharts", quietly = TRUE)
require(package = "pipeR", quietly = TRUE)
```

# Introduction

**rAmCharts** is an R package for interactive charts. It is based on the javascript library **amcharts.js** (https://amcharts.com). Currently it implements most of the functionnalities found in the distributions **CHARTS** and **STOCK CHARTS**. You'll find the source code and bug reports on our [github page][github_page], do not hesitate to send your bugs and your comments.

Based on [htmlwidgets][], it is compatible with [shiny][], R Markdown documents and RStudio viewer.

# Installation

Package is on CRAN.

```{r, eval=FALSE}
install.packages("rAmCharts")

# can have new features in developpement version 
devtools::install_github("dataknowledge/rAmCharts")
```

# Prerequisite

- Some functions import the package **rlist** refering to http://renkun.me/rlist.

- Besides, the package uses internally **pipeR** which is usefull to draw complex charts by keeping a certain level of readability in the code. The function mainly used is `%>>%` (or `pipeline()`) but the package allow to do many more, see the official tutorial at http://renkun.me/pipeR-tutorial.

For those who are not familiar with the 'pipe style' the following lines are equivalent:

```{r, eval=FALSE}
head(x = get("iris", "package:datasets"), n = 3)
# or
get("iris", "package:datasets") %>>% head(n = 3)
# or
pipeline(
  get("iris", "package:datasets"),
  head(n = 3)
)
```
```{r, echo=FALSE}
get("iris", "package:datasets") %>>% head(n = 3)
```

## Find help

- We have developped few examples in an app with [shiny][] and [shinydashboard][], run `runShinyExamples()'.

- If you have some questions about properties to custom a chart you may find solutions in the online amcharts API at 
https://docs.amcharts.com/3/


[htmlwidgets]:    http://www.htmlwidgets.org
[github_page]:    https://github.com/DataKnowledge/rAmCharts
[shiny]:          http://shiny.rstudio.com
[shinydashboard]: https://rstudio.github.io/shinydashboard