---
title: "DependenciesGraphs"
output: html_document
---

**DependenciesGraphs** is a R package for visualisation of dependencies. All the remarks and bugs returns are welcome on github : https://github.com/DataKnowledge/DependenciesGraphs.

## Installation

Package is actually only available on github. You can install it with :

```{r, eval=FALSE}
devtools::install_github("DataKnowledge/DependenciesGraphs")
```

## Minimal example

**DependenciesGraphs** make types of graphs :

#Dependdencies between functions in a package
Can choose a specific function
```{r}
require(DependenciesGraphs, quietly = TRUE)
library(plyr)

dep <- funDependencies("package:plyr","count")
plot(dep)

```




Can choose all functions in a specific package or environnement
```{r}
 dep <- envirDependencies("package:plyr")
 plot(dep,block=TRUE)
```

#Dependdencies between packages
```{r}
dep <- Pck.load.to.vis("plyr")
plot(dep)
```

##Shiny application for fast visualisation


```{r,eval=FALSE}
launch.app()
```



