---
title: "DependenciesGraphs"
output: html_document
---

**DependenciesGraphs** is a R package for visualisation of dependencies. All the remarks and bugs returns are welcome on github : https://github.com/DataKnowledge/DependenciesGraphs.

## Installation

Package is actually only available on github. You can install it with :

```{r,eval=FALSE}
devtools::install_github("DataKnowledge/DependenciesGraphs")
```



#**DependenciesGraphs** make differents types of graphs :

###Dependdencies between functions in a package
####Specific function
```{r,message=FALSE}
require(DependenciesGraphs)
library(plyr,quietly = TRUE)
dep <- funDependencies("package:plyr","count")
plot(dep)
```


<p><br><br><br><br></p>
####All functions in a specific package or environnement
```{r}
 dep <- envirDependencies("package:plyr")
 plot(dep,block=TRUE)
```

###Dependdencies between packages
```{r}
dep <- Pck.load.to.vis("plyr")
plot(dep)
```

###Shiny application for fast visualisation


```{r,eval=FALSE}
launch.app()
```



