---
title: "DependenciesGraphs"
output: html_document
---

**DependenciesGraphs** is a R package for dependencies visuallization. All the remarks and bugs are welcome on github : https://github.com/DataKnowledge/DependenciesGraphs.

## Installation

Package is actually only available on github. You can install it with :

```{r,eval=FALSE}
devtools::install_github("DataKnowledge/DependenciesGraphs")
```



#**DependenciesGraphs** make differents types of graphs :

###Dependencies between functions in a package
####From a specific function
```{r,message=FALSE}
require(DependenciesGraphs)

# you mus first loaded the target package using library
library(plyr,quietly = TRUE)
dep <- funDependencies("package:plyr","count")
plot(dep)
```


<p><br><br><br><br></p>
#### Between all functions
```{r}
 dep <- envirDependencies("package:plyr")
 plot(dep,block=TRUE)
```

###Dependencies between (installed) packages
```{r}
dep <- Pck.load.to.vis("plyr")
plot(dep)
```

```{r}
dep <- Pck.load.to.vis(c("htmlwidgets", "shiny"))
plot(dep)
```

###Explore your installed package daster with the Shiny application


```{r,eval=FALSE}
launch.app()
```



